Dependent Object Types

### 2012-08-30 doc/candidacy/report.tex
a bit more

A class template $\cls{x: S \sep \tup d}$ is closely related to a
translucent sum, except that it needs to be instantiated into an
object while a translucent sum is a module. Like in a translucent sum,
$\tup d$ binds term labels to values and type labels to types. The $x$
of type $S$ stands for the self, i.e.\ the object being constructed
from the template. Its scope is the bindings $\tup d$. Since the self
is explicitly typed, the bindings in class templates can freely refer
to each other (and even to themselves) via $x$, while recall that, in
translucent sums, only later fields can depend on earlier ones.

Contrasting concrete type bindings $\tup d$ used in class template
terms with type declarations $\tup D$ used in record and class types,
the possible type binders in type declarations are type aliases $=$,
new types $\expand$ and abstract types $<:$. Only the first two are
also concrete type binders available in type bindings of class
templates.

@@

In terms of theoretical results, the paper confirms type soundness of
the calculus and the undecidability of type checking.

>>>>

A class template $\cls{x: S \sep \tup d}$ is closely related to a
translucent sum, except that it needs to be instantiated into an
object while a translucent sum is a module. Like in a translucent sum,
$\tup d$ binds term labels to values and type labels to types. The $x$
of type $S$ stands for the self, i.e.\ the object being constructed
from the template. Its scope is the bindings $\tup d$. Since the self
is explicitly typed, the bindings in class templates can contractively
refer to each other (and even to themselves) via $x$, while recall
that, in translucent sums, only later fields can depend on earlier
ones.

Contrasting concrete type bindings $\tup d$ used in class template
terms with type declarations $\tup D$ used in record and class types,
the possible type binders in type declarations are type aliases $=$,
new types $\expand$ and abstract types $<:$. Only the first two are
also concrete type binders available in type bindings of class
templates. A consequence is that classes with abstract type members
cannot be instantiated, because each type declaration of the self type
needs to have a corresponding type binding when an object is
instantiated.

Mixing composition is not commutative. When expanding a type to a
record type, a compound type $R_1 \with R_2$ expands to a record type
containing the concatenation of the declarations in $R_1$ and $R_2$,
but if some label is defined in both $R_1$ and $R_2$, the definition
in $R_2$ overrides (and so must be more specific than) the definition
in $R_1$. Though this break of commutativity is justified from an
implementation standpoint, it is awkward from a typing standpoint: in
particular, it means that least upper bounds and greatest lower bounds
do not always exist.

@@

In terms of theoretical results, the paper confirms the type soundness
of the calculus and the undecidability of its type checking.
